---
title: "Final"
output:
  word_document: default
  html_document: default
date: "2022-12-13"
---

```{r}
round(runif(12, min = 0, max = 4), 2)
```
This is the randomly generated GPA.
```{r}
round(runif(12, min = 0, max = 30), 0)
```
This is the randomly generated days of school missed.
```{r}
round(runif(12, min = 0, max = 1), 0)
```
This is the randomly Are generated gender. 0 is women 1 is men.

The days missed have been x 4, then divide by 30 in order to match the scale. For class background 1 is yes and 0 is no.

x1: GPA = 2.53, Missed Days = 0.93, gender = 0
x2: GPA = 0.74, Missed Days = 1.07, gender = 1
x3: GPA = 3.74, Missed Days = 2.40, gender = 0
x4: GPA = 3.53, Missed Days = 0.93, gender = 0
x5: GPA = 2.36, Missed Days = 1.87, gender = 1
x6: GPA = 0.30, Missed Days = 2.40, gender = 0
x7: GPA = .56, Missed Days = 2.50, gender = 0
x8: GPA = 1.16, Missed Days = 2.50, gender = 1
x9: GPA = 0.53, Missed Days = 0, gender = 1
x10: GPA = 3.99, Missed Days = 0.26, gender = 0
x11: GPA = 2.21, Missed Days = 3.20, gender = 0
x12: GPA = 2.65, Missed Days = 0.53, gender = 0


Student x1 2.53 - 0.93 + 0 = 1.60. The 1.60 is the student's score. The higher the score, the more likely the student will score well on an assignment. On the opposite end the lower the score the more likely they will not do well on the assignment.

```{r}
1.60+0.67+1.34+2.60+1.49-2.10-1.94-.34+1.53+3.73-.99+2.09
9.68/12
```
```{r}
Mean <- 0.8066667

x1 <- 1.60 - Mean
x2 <- 0.67 - Mean
x3 <- 1.35 - Mean
x4 <- 2.60 - Mean
x5 <- 1.49 - Mean
x6 <- -2.10 - Mean
x7 <- -1.94 - Mean
x8 <- -.34 - Mean
x9 <- 1.53 - Mean
x10 <- 3.73 - Mean
x11 <- -0.99 - Mean
x12 <- 2.09 - Mean

x1
x2
x3
x4
x5
x6
x7
x8
x9
x10
x11
x12
```

If the variance is negative the student is below average and if it is positive the student is above average. Since we are trying to minimize the variance we need to see how far the variance is from zero. So we will have to take the absolute value


Objective: (Minimize) 0.79 S1G1 + 0.79 S1G2 + 0.79 S1G3 + 0.79 S1G4 + 0.13 S2G1 + 0.13 S2G2 + 0.13 S2G3 + 0.13 S2G4 + 0.54 S3G1 + 0.54 S3G2 + 0.54 S3G3 + 0.54 S3G4 + 1.79 S4G1 + 1.79 S4G2 + 1.79 S4G3 + 1.79 S4G4 + 0.68 S5G1 + 0.68 S5G2 + 0.68 S5G3 + 0.68 S5G4 + 2.91 S6G1 + 2.91 S6G2 + 2.91 S6G3 + 2.91 S6G4 + 2.75 S7G1 + 2.75 S7G2 + 2.75 S7G3 + 2.75 S7G4 + 1.15 S8G1 + 1.15 S8G2 + 1.15 S8G3 + 1.15 S8G4 + 0.72 S9G1 + 0.72 S9G2 + 0.72 S9G3 + 0.72 S9G3 + 2.92 S10G1 + 2.92 S10G2 + 2.92 S10G3 + 2.92 S10G4 + 1.80 S11G1 + 1.80 S11G2 + 1.80 S11G3 + 1.80 S11G4 + 1.28 S12G1 + 1.28 S12G2 + 1.28 S12G3 + 1.28 S12G4

S stands for the student number and G stands for the group number.

1. The total number of students in each group must be 3.

(Group 1) S1G1 + S2G1 + S3G1 + S4G1 + S5G1 + S6G1 + S7G1 + S8G1 + S9G1 + S10G1 + S11G1 + S12G1 = 3 Students

(Group 2) S1G2 + S2G2 + S3G2 + S4G2 + S5G2 + S6G2 + S7G2 + S8G2 + S9G2 + S10G2 + S11G2 + S12G2 = 3 Students

(Group 3) S1G3 + S2G3 + S3G3 + S4G3 + S5G3 + S6G3 + S7G3 + S8G3 + S9G3 + S10G3 + S11G3 + S12G3 = 3 Students

(Group 4) S1G4 + S2G4 + S3G4 + S4G4 + S5G4 + S6G4 + S7G4 + S8G4 + S9G4 + S10G4 + S11G4 + S12G4 = 3 Students

2. Only assigned one group.

S1G1 + S1G2 + S1G3 + S1G4 = 1
S2G1 + S2G2 + S2G3 + S2G4 = 1
S3G1 + S3G2 + S3G3 + S3G4 = 1
S4G1 + S4G2 + S4G3 + S4G4 = 1
S5G1 + S5G2 + S5G3 + S5G4 = 1
S6G1 + S6G2 + S6G3 + S6G4 = 1
S7G1 + S7G2 + S7G3 + S7G4 = 1
S8G1 + S8G2 + S8G3 + S8G4 = 1
S9G1 + S9G2 + S9G3 + S9G4 = 1
S10G1 + S10G2 + S10G3 + S10G4 = 1
S11G1 + S11G2 + S11G3 + S11G4 = 1
S12G1 + S12G2 + S12G3 + S12G4 = 1

3. Each student needs a group.

(S1G1 + S1G2 + S1G3 + S1G4) + (S2G1 + S2G2 + S2G3 + S2G4) + (S3G1 + S3G2 + S3G3 + S3G4) + (S4G1 + S4G2 + S4G3 + S4G4) + (S5G1 + S5G2 + S5G3 + S5G4) + (S6G1 + S6G2 + S6G3 + S6G4) + (S7G1 + S7G2 + S7G3 + S7G4) + (S8G1 + S8G2 + S8G3 + S8G4) + (S9G1 + S9G2 + S9G3 + S9G4) + (S10G1 + S10G2 + S10G3 + S10G4) + (S11G1 + S11G2 + S11G3 + S11G4) + (S12G1 + S12G2 + S12G3 + S12G4) = 12

4. The output must be binary.

1 = the student will be placed in the group
0 = the student will not be placed the group

5. Each group to be as equal as possible. The group variance should be as close to zero as possible.

(S1G1 + S2G1 + S3G1 + S4G1 + S5G1 + S6G1 + S7G1 + S8G1 + S9G1 + S10G1 + S11G1 + S12G1) - (S1G2 + S2G2 + S3G2 + S4G2 + S5G2 + S6G2 + S7G2 + S8G2 + S9G2 + S10G2 + S11G2 + S12G2) = 0

(S1G1 + S2G1 + S3G1 + S4G1 + S5G1 + S6G1 + S7G1 + S8G1 + S9G1 + S10G1 + S11G1 + S12G1) - (S1G3 + S2G3 + S3G3 + S4G3 + S5G3 + S6G3 + S7G3 + S8G3 + S9G3 + S10G3 + S11G3 + S12G3) = 0

(S1G1 + S2G1 + S3G1 + S4G1 + S5G1 + S6G1 + S7G1 + S8G1 + S9G1 + S10G1 + S11G1 + S12G1) - (S1G4 + S2G4 + S3G4 + S4G4 + S5G4 + S6G4 + S7G4 + S8G4 + S9G4 + S10G4 + S11G4 + S12G4) = 0

(S1G2 + S2G2 + S3G2 + S4G2 + S5G2 + S6G2 + S7G2 + S8G2 + S9G2 + S10G2 + S11G2 + S12G2) - (S1G3 + S2G3 + S3G3 + S4G3 + S5G3 + S6G3 + S7G3 + S8G3 + S9G3 + S10G3 + S11G3 + S12G3) = 0

(S1G2 + S2G2 + S3G2 + S4G2 + S5G2 + S6G2 + S7G2 + S8G2 + S9G2 + S10G2 + S11G2 + S12G2) - (S1G4 + S2G4 + S3G4 + S4G4 + S5G4 + S6G4 + S7G4 + S8G4 + S9G4 + S10G4 + S11G4 + S12G4) = 0

(S1G3 + S2G3 + S3G3 + S4G3 + S5G3 + S6G3 + S7G3 + S8G3 + S9G3 + S10G3 + S11G3 + S12G3) - (S1G4 + S2G4 + S3G4 + S4G4 + S5G4 + S6G4 + S7G4 + S8G4 + S9G4 + S10G4 + S11G4 + S12G4) = 0

```{r}
library(lpSolveAPI)
```


```{r}
lprec <- make.lp(0, 48)
set.objfn(lprec, c(.79,.79,.79,.79,0.13,0.13,0.13,0.13,0.54,0.54,0.54,0.54,1.79,1.79,1.79,1.79,.68,.68,.68,.68,2.90,2.90,2.90,2.90,2.75,2.75,2.75,2.75,1.15,1.15,1.15,1.15,0.72,0.72,0.72,0.72,2.92,2.92,2.92,2.92,1.80,1.80,1.80,1.80,1.28,1.28,1.28,1.28))
lp.control(lprec, sense = 'min', all.bin=TRUE)
```
```{r}
add.constraint(lprec, c(1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0), "=", 3)
add.constraint(lprec, c(0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0), "=", 3)
add.constraint(lprec, c(0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0), "=", 3)
add.constraint(lprec, c(0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1,0,0,0,1), "=", 3)
```
```{r}
add.constraint(lprec, c(1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "=", 1)
add.constraint(lprec, c(0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "=", 1)
add.constraint(lprec, c(0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "=", 1)
add.constraint(lprec, c(0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "=", 1)
add.constraint(lprec, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "=", 1)
add.constraint(lprec, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "=", 1)
add.constraint(lprec, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "=", 1)
add.constraint(lprec, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), "=", 1)
add.constraint(lprec, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0), "=", 1)
add.constraint(lprec, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0,0,0,0,0), "=", 1)
add.constraint(lprec, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,0,0,0,0), "=", 1)
add.constraint(lprec, c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1), "=", 1)
```
```{r}
add.constraint(lprec, c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1), "=", 12)
```
```{r}
add.constraint(lprec, c(1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0), "=", 0)
add.constraint(lprec, c(1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0), "=", 0)
add.constraint(lprec, c(1,0,0,-1,1,0,0,-1,1,0,0,-1,1,0,0,-1,1,0,0,-1,1,0,0,-1,1,0,0,-1,1,0,0,-1,1,0,0,-1,1,0,0,-1,1,0,0,-1,1,0,0,-1), "=", 0)
add.constraint(lprec, c(0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0), "=", 0)
add.constraint(lprec, c(0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1,0,1,0,-1), "=", 0)
add.constraint(lprec, c(0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1,0,0,1,-1), "=", 0)
```
```{r}
solve(lprec)
get.objective(lprec)
get.variables(lprec)
```

Group 1: 6, 7, 10
Average GPA: 1.66
Average days missed: 13
Gender: All women

Group 2: 4, 5, 11 
Average GPA: 2.31
Average days missed: 15
Gender: 2 women and 1 man

Group 3: 1, 8, 9
Average GPA: 1.41
Average days missed: 8.66
Gender: 1 women and 2 men

Group 4: 2, 3, 12
Average GPA: 2.37
Average days missed: 10
Gender: 2 women and 1 man
